---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# generics

[![Build Status](https://travis-ci.org/r-lib/generics.svg?branch=master)](https://travis-ci.org/r-lib/generics)
[![Coverage status](https://codecov.io/gh/r-lib/generics/branch/master/graph/badge.svg)](https://codecov.io/github/r-lib/generics?branch=master)
![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)

generics is designed to alleviate the situation where multiple packages define a generic with the same name. For example, if two packages define a `fit()` generic and methods, there will be conflicts when both packages are loaded. One approach would be for one package to import the other but this may result in many additional package dependencies during installation. 

## Installation

To install generics, use:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("r-lib/generics")
```

## Usage

generics is a simple, lightweight package that contains S3 generics to be used by other packages. Some examples are:

```{r}
library(generics)

fit

tidy
```

To use this in your package we recommend that you import and re-export the generics of interest. For example, if you want to provide a method for the  S3 `fit()` generic, you'd using the following the `roxygen2` code:

``` {r}
#' @importFrom generics explain
#' @export
generics::explain
```

As an example, the [recipes](https://github.com/tidymodels/recipes) package defines a number of `tidy()` S3 methods by importing this package (whereas it previously depended on `broom`). 

It is **also highly recommended** that you add an _alias_ in the documentation of your method for the generic, such as:

```{r}
#' @alias explain
```

In that way, when someone uses `?explain`, your specific method will show up as one of the man page options.  
