---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# generics

<!-- badges: start -->
[![R-CMD-check](https://github.com/r-lib/generics/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/generics/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/r-lib/generics/branch/main/graph/badge.svg)](https://app.codecov.io/gh/r-lib/generics?branch=main)
<!-- badges: end -->

`generics` is designed to help package authors reduce dependencies by providing a set of generic methods that can be imported. For example, if a package author wanted to include a `tidy` method for their object, they would have to import the `broom` package to do so. This would work but would potentially increase the number of package dependencies required to install and/or test the package. 

## Installation

To install `generics` from CRAN, use:

```{r, eval = FALSE}
install.packages("generics")
```

To install the development version, use:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("r-lib/generics")
```

## Usage

`generics` is a simple, lightweight package that contains S3 generics to be used by other packages. Some examples are:

```{r}
library(generics)

fit

tidy
```

To use `generics` with your package, we recommend that you import and re-export the generic(s) of interest. For example, if you want to provide a method for the  S3 `explain()` method, you'd using the following `roxygen2` code:

``` {r, eval = FALSE}
#' @importFrom generics explain
#' @export
generics::explain
```

As an example, the [recipes](https://github.com/tidymodels/recipes) package defines a number of `tidy()` S3 methods by importing this package (whereas it previously depended on `broom`). 

## Documentation

When searching for help on a method that is exported from `generics` by one or more packages, using `?method` will show entries for all exported methods. If the version from `generics` is selected, the Methods section dynamically lists all specific methods exported by any loaded packages. 
